
\documentclass[11pt,article,oneside]{memoir}
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{setspace}

% margins
\usepackage[left=1.5in, right=1.75in, top=1in, bottom=0.75in]{geometry}% adjust the page margins

\RequirePackage{xcolor}
\definecolor{CornellRed}{HTML}{b31b1b} % official Cornell red color -- use for text etc
\definecolor{CornellGray}{HTML}{222222} % official Cornell gray -- use for Section
\definecolor{LightGray}{HTML}{F7F7F7} % background color -- do not use for anything else
\definecolor{BrickRed}{HTML}{C04829} % backup color
\definecolor{GrassGreen}{HTML}{359245}
\definecolor{WarmYellow}{HTML}{E9A139}

%% Choose fonts for use with xelatex
\usepackage{fontspec}
\setmainfont[Path=fonts/,
Mapping={tex-text},
Numbers={OldStyle},
Ligatures={Common},
UprightFont=*-Regular,
BoldFont=*-Bold,
ItalicFont=*-Italic,
BoldItalicFont=*-BoldItalic
]{CrimsonText}
\setsansfont[Path=fonts/,
Mapping=tex-text,
Colour=b31b1b,
UprightFont=*-Regular,
BoldFont=*-Bold,
ItalicFont=*-Italic]{Lato}
\setmonofont[Path=fonts/,
Mapping=tex-text,
Scale=0.9,
UprightFont=*-Regular]{Inconsolata}

%%------------------------------------------------------------------------
%% Section styling
%%------------------------------------------------------------------------

%% This includes a fudge from the following link in order to get the
%% subsection to align with a section
%% http://tex.stackexchange.com/questions/19200/titlesec-remove-space-after-empty-margin-section

\makeatletter
\newif\ifaftersec\aftersecfalse

\newcommand\setsubskip{%
    \global\aftersectrue
    \everypar{%
        \global\aftersecfalse
        \if@noskipsec
            \global\@noskipsecfalse
            \clubpenalty\@M
            \hskip-\parindent
            \begingroup
                \@svsechd\unskip{\hspace{\@tempskipb}}%
            \endgroup
        \else
            \clubpenalty\@clubpenalty\everypar{}%
        \fi}}

\newcommand\subskip{%
  \ifaftersec
     \removelastskip%
     \vspace{-\baselineskip}
  \fi
  \global\aftersecfalse}

% Section styling
\titleformat{\section}[leftmargin]{\raggedleft\sffamily\bfseries\footnotesize}{}{0pt}{}[\setsubskip]
\titlespacing*{\section}{2cm}{1ex}{0.25in}

% Subsection styling
\titleformat{\subsection}{\subskip\itshape}{}{0pt}{}[]
\titlespacing*{\subsection}{0em}{2.5ex}{1ex}

\raggedbottom
\makeatother

% useful macro
\newcommand{\dotspace}{\quad}

% better lists
\usepackage{enumitem}
\setlist[itemize, 1]{nosep, noitemsep, labelsep=-5pt, leftmargin=*, after=\vspace{\baselineskip}, itemindent=-15pt, labelindent=5pt}

% Use BibLaTeX
\usepackage[autostyle=true, autopunct=true, english=american]{csquotes}

%% other stuff
% icons for the contact info
\usepackage{fontawesome5}
\usepackage{academicons}

% macros and environments
\newcommand{\Header}[1]{\\\multicolumn{3}{L{7in}}{\color{BrickRed}\Large{\spacedlowsmallcaps{#1}}}\\}
\newcommand{\Publication}[1]{\fullcite{#1} & \citeyear{#1}}
\newcommand{\CVEntry}[3]{#1 & #2 & #3}
\newenvironment{cv}
{
	\noindent\begin{longtable}{ >{\em}R{1in} L{5in} >{\em}R{0.875in} }
}{
    \end{longtable}
}

\usepackage{fancyhdr}
\usepackage[yyyymmdd,hhmmss]{datetime}
\pagestyle{fancy}
\rfoot{Current as of \today}
\cfoot{}
\lfoot{Page \thepage}

\renewcommand{\headrulewidth}{0pt}
\fancyhead{}

% have to load this last
\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=CornellRed, linkcolor=CornellRed, pdfnewwindow=true}

%% ------------------------------------------------------------------------
%%   Bibliography formatting
%% ------------------------------------------------------------------------
%% documentation:
%% http://ctan.mirrorcatalogs.com/macros/latex/exptl/biblatex/doc/biblatex.pdf
% Use BibLaTeX
\usepackage[
	backend=biber,
	style=publist,
	plauthorfirstinit=true,
	plauthorhandling=highlight,
	plnumbering=none,
	labeldateparts=false,
	linktitles={none, doi, url},
	hlyear=true,
	marginyear=false,
	doi=true,
	url=false,
	isbn=false,
	maxbibnames=99,
	maxcitenames=99,
  giveninits,
	date=year
]{biblatex}

\AtEveryBibitem{%
  \clearlist{language}%
}

% specify sorting rules
\DeclareSortingTemplate{ndymdt}{
  \sort{
    \field{presort}
  }
  \sort[final]{
    \field{sortkey}
  }
  \sort{
    \field{sortname}
    \field{author}
    \field{editor}
    \field{translator}
    \field{sorttitle}
    \field{title}
  }
  \sort[direction=descending]{
    \field{sortyear}
    \field{year}
    \literal{9999}
  }
  \sort[direction=descending]{
    \field[padside=left,padwidth=2,padchar=0]{month}
    \literal{99}
  }
  \sort[direction=descending]{
    \field[padside=left,padwidth=2,padchar=0]{day}
    \literal{99}
  }
  \sort{
    \field{sorttitle}
  }
  \sort[direction=descending]{
    \field[padside=left,padwidth=4,padchar=0]{volume}
    \literal{9999}
  }
}


\setlength{\bibhang}{15pt}

% add bib resources


\addbibresource{bibliography/library.bib}

\addbibresource{bibliography/conferences.bib}


% bold my name
\plauthorname[Vivek]{Srikrishnan}

% Format sub-bibliography headings as subsections
\defbibheading{subbibliography}[\refname]{\subsection*{#1}}

% remove period inbetween volume and number
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}%
%  \setunit*{\adddot}% DELETED
  \setunit*{\addnbspace}% NEW (optional); there's also \addnbthinspace
  \printfield{number}%
  \setunit{\addcomma\space}%
  \printfield{eid}%
}

\DeclareFieldFormat
  [article,inbook,incollection,inproceedings,patent,thesis,
   unpublished,report,techreport,misc,book]
  {title}{\mkbibquote{#1}}
\DeclareFieldFormat{url}{\url{#1}}
\DeclareFieldFormat[article]{pages}{#1}
\DeclareFieldFormat[inproceedings]{pages}{\lowercase{pp.}#1}
\DeclareFieldFormat[incollection]{pages}{\lowercase{pp.}#1}
\DeclareFieldFormat[article]{volume}{\mkbibbold{#1}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\DeclareFieldFormat[article]{url}{}
\DeclareFieldFormat{notes}{#1}
\DeclareFieldFormat{shorthandwidth}{#1}
\DeclareFieldFormat{extrayear}{}
    
% Remove In: for an article.
\renewbibmacro{in:}{%
  \ifentrytype{article}{}{%
  \printtext{\bibstring{in}\intitlepunct}}}

% Bibliography categories
\def\makebibcategory#1#2{\DeclareBibliographyCategory{#1}\defbibheading{#1}{\subsection*{#2}}}
\makebibcategory{papers}{Journal articles}
\makebibcategory{inpress}{Under Review and In Press}
\makebibcategory{conferences}{Conference Proceedings}
\makebibcategory{books}{Books}
\makebibcategory{chapters}{Book Chapters}
\makebibcategory{techreport}{Reports}
\makebibcategory{talks}{Conference Talks}
\makebibcategory{posters}{Conference Posters}
\makebibcategory{software}{Software}
\makebibcategory{bookreviews}{Book reviews}
\makebibcategory{editorials}{Editorials}
\makebibcategory{phd}{PhD thesis}

\setlength{\bibitemsep}{2.5pt}

%\renewcommand*{\bibitem}{\item \mbox{} \\}
%\defbibenvironment{bibliography}
%{\list{}
%  {\setlength{\leftmargin}{\bibhang}%
%   \setlength{\itemsep}{\bibitemsep}%
%   \setlength{\parsep}{\bibparsep}}}
%{\endlist}
%{\bibitem}

\newenvironment{publications}{\section{Publications}}

\def\printbib#1{\printbibliography[category=#1,heading=#1]}
%\renewcommand{\bibfont}{\normalfont\fontsize{11}{13.4}\rmfamily}

% Add all papers in the bib file.
\nocite{*}


%---------------------------------------------------------------------

\begin{document}

%% Name and contact block

\begin{minipage}[t]{2.8in}
 \flushright {\footnotesize
 \href{http://ise.ncsu.edu}{Edward P. Fitts Department of Industrial and Systems Engineering}\\ \vspace{0in}
 915 Partners Way, 4171\\ \vspace{0in} North Carolina State University \\ \vspace{-0.04in} Raleigh, NC 27606, USA}
 \end{minipage}
 \begin{minipage}[t]{2.5in}
   \flushright {\footnotesize  \texttt{\href{mailto:barachun@ncsu.edu}{barachun@ncsu.edu}} \, \faEnvelope} \\ \vspace{-0.21in}
   \flushright {\footnotesize  \texttt{\href{http://resilience.wordpress.ncsu.edu}{http://resilience.wordpress.ncsu.edu}} \, \faGlobe} \\ \vspace{-0.195in}
   \flushright {\footnotesize
   \texttt{\href{https://github.com/brachunok}{brachunok}} \, \faGithub} \\ \vspace{-0.2in}
   \flushright {\footnotesize
   \texttt{\href{https://scholar.google.com/citations?user=Ct3IhL-MAAAAJ}{Ben Rachunok}} \, \aiGoogleScholar}

 \end{minipage}

 \bigskip

 %% Name
 \noindent{\LARGE\bfseries \textcolor{CornellGray}{Ben Rachunok}}
 \reversemarginpar

\bigskip

%% Research Interests

\section{research interests}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Climate risk management

\item Coupled natural-human systems

\item Complex system dynamics

\item Decision-making under uncertainty

\item Uncertainty characterization

\end{itemize}

%% Appointments

\section{appointments}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Assistant Professor, Department of Biological \& Environmental Engineering, Cornell University, 2021--present

\item Visiting Assistant Professor, Department of Biological \& Environmental Engineering, Cornell University, 2020--2021

\item Assistant Research Professor, Earth \& Environmental Systems Institute, Pennsylvania State University, 2019--2021

\item Postdoctoral Scholar, Earth \& Environmental Systems Institute, Pennsylvania State University, 2018--2019

\end{itemize}

%% Education

\section{education}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Ph.D., Energy \& Mineral Engineering, Pennsylvania State University, 2018

\item M.S., Energy \& Mineral Engineering, Pennsylvania State University, 2015

\item B.S., Mathematics, University of Illinois at Urbana-Champaign, 2004

\item B.A., Philosophy, University of Illinois at Urbana-Champaign, 2004

\end{itemize}

%% Publications
\section{publications}
\uspunctuation

\printbibliography[type=article, title={Peer-Reviewed Journal Articles}, heading=subbibliography]

\printbibliography[type=misc, title={Articles Under Review or Forthcoming}, heading=subbibliography, keyword=unpublished, resetnumbers]

\printbibliography[type=report, title={Reports}, heading=subbibliography, resetnumbers]

\printbibliography[type=book, title={Books}, heading=subbibliography, resetnumbers]

\printbibliography[type=inproceedings, title={Conference Proceedings}, heading=subbibliography, resetnumbers]

\printbibliography[type=misc, title={Conference Presentations}, heading=subbibliography, keyword=talk, resetnumbers]

\printbibliography[type=misc, title={Conference Posters}, heading=subbibliography, keyword=poster, resetnumbers]

%% Invited Talks

\section{invited talks}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item \enquote{Interplay of Emissions and Geophyiscal Uncertainties for Future Sea-Level Rise}, Civil and Environmental Engineering Seminar,  Rice University. Houston (TX), USA. Oct. 2024.

\item \enquote{Impacts of Emissions Uncertainties on Antarctic Instabilities and Sea-Level Rise}, Civil and Environmental Engineering Seminar,  Syracuse University. Syracuse (NY), USA. Mar. 2024.

\item \enquote{Impacts of Emissions Uncertainties on Antarctic Instabilities and Sea-Level Rise}, Environmental Science Seminar,  Baylor University. Waco (TX), USA. Feb. 2024.

\item \enquote{Navigating (Deep) Uncertainties in Climate Risk Management}, RIT Mathematical Modeling Seminar,  Rochester Institute of Technology. Rochester (NY), USA. Oct. 2023.

\item \enquote{How Uncertainties Can Impact Climate Risk Management}, Earth and Atmospheric Sciences Seminar,  Cornell University. Ithaca (NY), USA. Feb. 2023.

\item \enquote{An Introduction to Climate Risk Management}, Climate Change Seminar,  Cornell University. Ithaca (NY), USA. Jan. 2023.

\item \enquote{Identifying Challenges and Opportunities for Uncertainty Analysis in MultiSector Dynamics Research}, Community Webinar,  MultiSector Dynamics Community of Practice. remote. Oct. 2022 (with Jonathan Lamontagne).

\item \enquote{Considerations for Uncertainty in MultiSector Systems}, Cornell Energy Systems Institute Seminar,  Cornell University. Ithaca (NY), USA. Oct. 2022.

\item \enquote{Climate Risk, Uncertainty, and Coupled Energy Systems}, New Energy Series, Irving Institute,  Dartmouth College. Remote. Jan. 2022.

\item \enquote{Uncertainty and Climate Risk Management}, Center for Applied Mathematics Colloquium,  Cornell University. Ithaca (NY), USA. Nov. 2021.

\item \enquote{A Systems Approach to Climate Risk Management}, Ezra's Round Table,  Cornell University. Ithaca (NY), USA. Sep. 2021.

\item \enquote{How Likely Are the Most Extreme CO$_2$ Emissions Scenarios?}, MIT Joint Program on the Science and Policy of Global Change Seminar,  Massachusetts Institute of Technology. Remote. Aug. 2020.

\item \enquote{How Likely Are the Most Extreme CO$_2$ Emissions Scenarios?}, Energy and Environmental Economics and Policy Seminar,  Pennsylvania State University. University Park (PA), USA. Feb. 2020.

\item \enquote{Climate Risk Management: A Decision-Centered Approach}, Tufts Civil and Environmental Engineering Seminar,  Tufts University. Medford (MA), USA. Nov. 2019.

\item \enquote{Adaptive Multi-Objective Robust Decision-Making}, Carnegie Mellon-Penn State Workshop on Multi-Objective Robust Decision-Making,  Pennsylvania State University. University Park (PA), USA. Aug. 2019.

\item \enquote{From Earth-System Science to Coastal Hazards and Back}, Environmental and Sustainability Seminar,  Carnegie Mellon University. Pittsburgh (PA), USA. May 2019 (with Klaus Keller).

\item \enquote{Agent-Based Models: The New 'Plastic' or the Emperor's Clothes?}, Program on Coupled Natural-Human Systems Research Seminar,  Pennsylvania State University. University Park (PA), USA. Mar. 2019 (with Klaus Keller).

\item \enquote{From Earth-System Science to Coastal Hazards and Back},  Pacific Northwest National Laboratory. Richland (WA), USA. Mar. 2019 (with Klaus Keller).

\item \enquote{From Earth-System Science to Coastal Hazards and Back},  Joint Global Change Research Institute. College Park (MD), USA. Feb. 2019 (with Klaus Keller).

\item \enquote{Can We Avoid a (Rational) Route to Collapse?}, Workshop on Managing Natural Resource Risk in the Modern and Prehistoric World,  Santa Fe Institute. Santa Fe (NM), USA. Oct. 2018 (with Klaus Keller).

\item \enquote{Hedging Strategies for Electricity Investment Decisions Under Policy Uncertainty}, Energy and Mineral Engineering Graduate Seminar,  Pennsylvania State University. University Park (PA), USA. Mar. 2016.

\end{itemize}


%% Grants and Contracts

\section{grants and contracts}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Co-PI, \enquote{Valuing Hydropower Contributions Across Multiple Timescales}.  PI: Patrick Reed. NREL, \$16,556 (total: \$90,000). 2024--2024.

\item Co-PI, \enquote{Addressing Deep Uncertainty in Hydropower Futures}.  PI: Patrick Reed. NREL, \$15,053 (total: \$75,000). 2022--2023.

\item Investigator, Site Lead, \enquote{Understanding Multistressor and Multiscale Drivers of Feedbacks, Cascading Failures, and Risk Management Pathways within Complex MSD Systems}.  PI: Karen Fisher-Vanden. DOE (BER), \$533,922. 2021--2026.

\item Co-PI, \enquote{Health Effects of Decarbonization (HEALED)}.  PI: Wei Peng. NSF, \$50,001 (total: \$399,472). 2021--2024.

\item Investigator, Site Lead, Task Lead, \enquote{Integrated Coastal Modeling (ICoM)}.  PI: Ian Kraucunas. DOE (BER), \$598,217. 2021--2024.

\item Investigator, \enquote{Integrated Multi-Scale Multi-Sector Modeling (IM3)}.  PI: Jennie Rice. DOE (BER), \$25,000. 2019--2020.

\end{itemize}

%% Networks and Projects

\section{networks and projects}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Project on Coupled Human and Earth Systems (PCHES-ADAPT). Senior Personnel. PI: Karen Fisher-Vanden, Robert Nicholas, and John Weyant. Department of Energy, Biological and Environmental Research. 2021--current.

\item Integrated Coastal Modeling (ICoM). Task Lead. PI: Ian Kraucunas. Department of Energy, Biological and Environmental Research. 2019--current.

\item Visualizing Forest Futures (ViFF). Participant. PI: Erica Smithwick. National Science Foundation. 2019--2021.

\item Project on Coupled Human and Earth Systems (PCHES-FRAME). Participant. PI: Karen Fisher-Vanden and John Weyant. Department of Energy, Biological and Environmental Research. 2018--2021.

\item Network for Sustainable Climate Risk Management (SCRiM). Participant. PI: Klaus Keller. National Science Foundation. 2016--2019.

\end{itemize}

%% Teaching

\section{teaching}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\vspace{\baselineskip}



\subsection{Cornell University}
\begin{itemize}[label={}]

\item BEE 4850/5850 --- Environmental Data Analysis and Simulation. Primary Instructor. Spring 2024.

\item BEE 2000 --- Perspectives on the Climate Change Challenge. Collaborative Instructor. Spring 2024.

\item BEE 4750/5750 --- Environmental Systems Analysis. Primary Instructor. Fall 2022, 2023.

\item BEE 6940 --- Climate Risk Analysis. Primary Instructor. Spring 2023.

\item BEE 6940/AAP Design Studio --- Climate Uncertainties. Collaborative Instructor. Fall 2023.

\end{itemize}

\subsection{Pennsylvania State University}
\begin{itemize}[label={}]

\item EME 301 --- Thermodynamics in Energy and Mineral Engineering. Teaching Assistant. Fall and Spring 2014, 2015, 2016.

\item Math 140 --- Calculus with Analytic Geometry I. Primary Instructor. Spring 2011.

\item Math 411 --- Ordinary Differential Equations. Primary Instructor. Summer 2008, 2010.

\item Math 232 --- Integral Vector Calculus. Primary Instructor. Spring 2010.

\item Math 41 --- Trigonometry and Analytic Geometry. Primary Instructor. Fall 2005, 2010.

\item Math 251 --- Ordinary and Partial Differential Equations. Primary Instructor. Fall and Spring 2007, 2008, 2009.

\item Math 141 --- Calculus with Analytic Geometry II. Primary Instructor. Fall 2009.

\item Math 497 --- Symplectic Geometry. Teaching Assistant. Fall 2008.

\item Math 250 --- Ordinary Differential Equations. Primary Instructor. Fall 2006.

\item Math 231 --- Calculus of Several Variables. Primary Instructor. Fall and Spring 2004, 2006.

\end{itemize}


%% Workshops

\section{workshops organized}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Climate Risk Management Summer Fest. Hanover (NH), USA. Aug. 2024.

\item Carnegie Mellon-Penn State Workshop on Multi-Objective Robust Decision-Making. University Park (PA), USA. Aug. 2019.

\end{itemize}


%% Advising

\section{advising}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\vspace{\baselineskip}


\subsection{Postdoctoral}
\begin{itemize}[label={}]


\item Elnaz Kabir. Decarbonized Energy System Operations. Co-advised with C. Lindsay Anderson \& Scott Steinschneider. 2021--2023.  Current: Assistant Professor, Engineering Technology \& Industrial Distribution, Texas A\&M.


\end{itemize}

\subsection{Graduate}
\begin{itemize}[label={}]


\item Yifan Luo. Ph.D., Civil \& Environmental Engineering. Advisor, Committee Chair. 2023--present.  

\item Katerina Tang. Ph.D., Applied Mathematics. Advisor. 2022--present.  

\item Parin Bhaduri. Ph.D., Biological \& Environmental Engineering. Advisor, Committee Chair. 2021--present.  

\item Demola Ogunnaike. M.S., Civil \& Environmental Engineering. . 2024--present.  

\item Gabriela Ackermann Logan. M.S., Biological \& Environmental Engineering. Advisor, Committee Chair. 2023--present.  

\item Chloe Darnell. M.S., Biological \& Environmental Engineering. Advisor, Committee Chair. 2021--2023.  Thesis: "Uncertainty in emissions pathways and earth system dynamics: implications for global mean sea level rise." 

\item Carl Frederick Aquino. M.S., Geosciences. Co-Advisor. 2020--2022.  Thesis: "Greenland ice sheet drives sea-level rise differences between model and expert projections." 

\item Nicole Rosario Nieves. M.Eng., Biological \& Environmental Engineering. Advisor. 2023--2023.  Thesis: "Generation of an agent-based policy tree for decision making on home elevation in coastal floodable areas." 


\end{itemize}

\subsection{Undergraduate}
\begin{itemize}[label={}]


\item Cella Schnabel. Civil \& Environmental Engineering. Research Advisor. 2023--present.  

\item Cannon Cline. Earth \& Atmospheric Science. Research Advisor. 2023--present.  

\item Matthew Lipton. Biological \& Environmental Engineering. Research Co-Advisor (with C. Lindsay Anderson). 2023--2023.  


\end{itemize}


%% Committee Membership

\section{committee member}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\vspace{\baselineskip}
\begin{itemize}[label={}]

\item Trevor Amestoy, Ph.D., Civil \& Environmental Engineering. current.

\item Lillian Lau, Ph.D., Civil \& Environmental Engineering. current.

\item Kaleb Smith, Ph.D., Civil \& Environmental Engineering. current.

\item Jingya Han, Ph.D., Atmospheric Science. current.

\item Taylor Fernandes Nunez, Ph.D., Applied Mathematics. current.

\item Richard Toohey, Ph.D., Atmospheric Science. current.

\end{itemize}


%% Awards

\section{awards}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Graduate Research Fellowship Honorable Mention, National Science Foundation. 2015

\item Harold F. Martin Graduate Assistant Outstanding Teaching Award, Pennsylvania State University Graduate School. 2011

\item Charles H. Hoover Memorial Award, Pennsylvania State University Department of Mathematics. 2010

\item Departmental Teaching Award, Pennsylvania State University Department of Mathematics. 2008

\item ZZRQ Award, Pennsylvania State University Department of Mathematics. 2006

\end{itemize}

%% Outreach

\section{outreach}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Taught session on multi-objective robust decision-making, SCRiM/Dartmouth Summer School. 2018, 2019, 2023.

\end{itemize}

%% Service

\section{service}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Co-Organizer and Session Chair, Energy Modeling Forum Snowmass Workshop. 2023--present.

\item Faculty Fellow, Cornell Atkinson Center for a Sustainable Future. .

\item Co-Organizer, BEE Department Seminar. 2021--present.

\item Associate Deputy Editor, \emph{Climatic Change}.  2021--present.

\item Early Career Researcher Board Member, \emph{Oxford Open Energy}.  2022--present.

\item Co-Chair, MultiSector Dynamics Working Group on Uncertainty Quantification and Scenario Development. 2019--present.

\item Member, MultiSector Dynamics Community of Practice Scientific Steering Group. 2019--present.

\item Co-Convener and Co-Chair, AGU Sessions on MultiSector Dynamics and Uncertainty. 2020--2024.

\item Co-Convener, European Social Simulation Association Meeting Session on Uncertainty in Agent-Based simulation. 2024.

\item Co-Guest Editor, \emph{Water}. Special Issue on 'Climate Model Projections: Sea-Level Rise and Impacts on Coastal Defense Decision-Making'. .

\item Panel Reviewer, National Science Foundation (HDBE), Department of Energy (BER). .

\item Ad Hoc Reviewer, Sloan Foundation, National Science Foundation (DRMS, MG\&G), Austrian Science Fund. .

\item Member, Environmental Engineering Program Curriculum Committee. Fall 2022--present.

\item Member, Biological \& Environmental Engineering Faculty Search Committees. 2022, 2024.

\end{itemize}

%% Professional Experience

\section{professional experience}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]

\item Research Assistant, Brownson Solar Research Group, Pennsylvania State University. 2011--2014

\item Technical Editor, Journal of Modern Dynamics. 2008--2010

\end{itemize}



\end{document}